---
title: Example manuscript using the *preprint* Quarto template that tests various features
running-head: Running head
author:
  - name: Matti Vuorre
    email: mjvuorre@uvt.nl
    orcid: 0000-0001-5052-066X
    url: https://www.tilburguniversity.edu/staff/m-j-vuorre
    corresponding: true
    affiliation:
      - ref: 1
  - name: Author Number Two
    equal-contributor: true
    affiliation:
      - ref: 1
      - ref: 2
  - name: Author Three
    affiliation:
      - ref: 3
affiliations:
  - id: 1
    name: Tilburg University
    department: Department of Social Psychology
  - id: 2
    name: Other institution
    department: Other department
  - id: 3
    name: Third institution has no department
abstract: |
  This manuscript and its source (`example.qmd`) illustrate use of various [Quarto](https://quarto.org) & *preprint* template features.

  XOXO offal biodiesel adaptogen normcore listicle, hot chicken adipisicing readymade ascot mukbang anim lyft cold-pressed [@r2024]. Gorpcore DIY vice, id la croix aliqua williamsburg occaecat wayfarers health goth wolf ut post-ironic DSA flexitarian. Subway tile hexagon try-hard drinking vinegar taiyaki vice portland eu semiotics paleo butcher small batch cred enim selvage.
keywords: 
  - list 
  - keywords
  - here
license: CC BY
date: 2024-06-12
citation:
  type: article-journal
  container-title: "PsyArXiv"
  doi: "10.31234/osf.io/z3ejx"
  url: https://osf.io/preprints/psyarxiv/z3ejx
authornote: This is an example author note.
bibliography: bibliography.bib
bibliographystyle: apa
toc: false
linkcolor: rgb(0, 0, 255)
section-numbering: "1.1"
bibliography-title: "Works referred to"
mainfont: Libertinus Serif
fontsize: 12pt
execute: 
  cache: true
format:
  preprint-typst: 
    papersize: us-letter
    keep-typ: true
    margin:
      x: 3cm
      y: 2.5cm
code-links: repo
---

# Introduction

Pariatur laboris four dollar toast wayfarers solarpunk keffiyeh edison bulb grailed letterpress schlitz cloud bread taiyaki messenger bag raw denim. Four dollar toast cold-pressed enamel pin disrupt gatekeep hexagon fam. 

Brooklyn sed chia trust fund copper mug. Live-edge meditation small batch jean shorts 8-bit, semiotics tilde craft beer try-hard big mood. Officia gluten-free snackwave fit, adaptogen blog chia keytar austin ullamco aliquip.

## A detailed point

Gatekeep single-origin coffee yes plz marxism, same literally eiusmod fingerstache live-edge blackbird spyplane kogi ullamco hashtag laboris. Forage marxism in poke edison bulb try-hard tacos irony raclette. Tonx mukbang mlkshk roof party bitters, taxidermy gastropub nulla. Locavore godard tbh unicorn eiusmod poutine. Gochujang gluten-free letterpress, palo santo tumeric sint echo park paleo gorpcore tumblr Brooklyn offal eiusmod pop-up cloud bread. Elit big mood edison bulb, artisan esse et marxism neutral milk hotel slow-carb grailed flannel farm-to-table kombucha (@fig-example).

```{r}
#| label: fig-example
#| fig-cap: This is an example scatterplot from R source.
#| fig-height: 4
#| fig-width: 4
#| echo: false

set.seed(1)
data <- data.frame(x = rnorm(30), y = rnorm(30))
plot(data)
```

::: {.callout-note}
This document is silly---it just allows testing that Quarto features and metadata are appropriately handled. Like inline LaTeX math ($\eta = \text{something}+\frac{\alpha}{\beta} + 1$), basic markdown (**bold text**), and footnotes[^1].
:::

[^1]: Footnote!

### Unnecessary detail

Poutine synth kombucha fanny pack fit hot chicken cornhole taiyaki pour-over copper mug nostrud ascot food truck. Taxidermy viral post-ironic irony, JOMO jawn whatever gorpcore PBR&B. Distillery pickled duis man braid poke master cleanse marfa skateboard. Hell of taiyaki lorem, cliche vegan praxis etsy kale chips humblebrag (@tbl-example).

```{r}
#| label: tbl-example
#| tbl-cap: Tables created with `tinytable::tt()`, `knitr::kable()`, etc also work (footnotes don't).

tinytable::tt(
  head(data),
  digits = 2, 
)
```

Offal tumeric adaptogen chartreuse in squid art party. Seitan chartreuse laborum, bruh hot chicken swag truffaut XOXO commodo ipsum excepteur big mood cliche venmo. Celiac jawn sint gentrify, mumblecore skateboard hexagon. Lorem vinyl kinfolk, blog artisan yr hexagon try-hard activated charcoal. Pop-up snackwave cred literally tousled, praxis marxism coloring book bespoke palo santo.
