---
title: "*quarto-preprint*: An example document"
running-head: "*quarto-preprint*"
author:
  - name: Matti Vuorre
    email: mjvuorre@uvt.nl
    orcid: 0000-0001-5052-066X
    url: https://www.tilburguniversity.edu/staff/m-j-vuorre
    corresponding: true
    equal-contributor: true
    affiliation:
      - ref: 1
  - name: Second Author
    email: mail@example.com
    orcid: 0000-0001-5052-066X
    url: https://www.tilburguniversity.edu/staff/m-j-vuorre
    equal-contributor: true
    affiliation:
      - ref: 2
      - ref: 3
affiliations:
  - id: 1
    name: Tilburg University
    department: Department of Social Psychology
  - id: 2
    name: Example Institution
    department: Department of Examples
  - id: 3
    name: Example Second Institution
    department: Department of Examples
abstract: |
  This is an example Quarto document using the `preprint-typst` format.
categories: [Quarto, Typst, extension, preprint]
date: "`r Sys.Date()`"
bibliography: bibliography.bib
csl: https://www.zotero.org/styles/apa
authornote: This is an example author note.
wordcount: true
functions: [place, appendix]
format: preprint-typst
---

# Introduction

This is an example `preprint-typst` document. Let us first take a look at body text and headings.

{{< lipsum 1 >}}[^fn-1]

[^fn-1]: This is a footnote.

## Heading level 2

### Heading level 3

#### Heading level 4

Level 4 and 5 headers are in paragraph.

##### Heading level 5

Level 5 header is indented.

## Floats

### Tables

```{r}
#| include: false

set.seed(1)
data <- data.frame(x = rnorm(30), y = rnorm(30))
```

Here is an example table (@tbl-example).

```{r}
#| label: tbl-example
#| tbl-cap: Table created with `knitr::kable()`.
#| echo: false

knitr::kable(
  head(data, 2),
  digits = 2
)
```

### Figures

::: {#fig-1}
{{< placeholder 400 200 format=svg >}}
:::

@fig-1 is a figure.

### Full-width content

You can also include page-wide figures (or any other content) in documents that have more than one column. See @fig-2 for an example. First, include

```yaml
functions: place
```

in the document's YAML. Then, wrap your figure in a Quarto div[^fn0] like this:

```
::: {.place arguments='auto, scope: "parent", float: true'}
Everything here will span the whole page.
:::
```

The above uses the Typst's `place()`[^fn1] function through the typst-function[^fn2] Quarto extension to place the div's content in `"parent"` scope (the document page is the column's parent) and must specify that Typst should treat the content as a float. `auto` indicates where the figure should be on the page, and can be either `auto`, `bottom`, or `top`. (Note `auto` and `bottom` can make the figure appear below footnotes.)

:::: {.place arguments='auto, scope: "parent", float: true'}
::: {#fig-2}
{{< placeholder 600 100 format=svg >}}
:::
::::

[^fn0]: <https://quarto.org/docs/authoring/markdown-basics.html#sec-divs-and-spans>
[^fn1]: <https://typst.app/docs/reference/layout/place/>
[^fn2]: <https://github.com/christopherkenny/typst-function>

## Quarto markdown features

### Maths

LaTeX math notation is automatically converted to Typst and as such works just fine either inline ($y_i = \alpha + \beta x_i + \epsilon_i$) or in display mode (@eq-1).

$$
f(x \mid \mu, \sigma^2) = \frac{1}{\sqrt{2\pi \sigma^2}} \exp\left(-\frac{(x-\mu)^2}{2\sigma^2}\right)
$$ {#eq-1}

### Block quotes

To insert a block quote, prepend a paragraph with `>`:

>A quote: "*Elit ullamcorper dignissim cras tincidunt lobortis feugiat vivamus at.*"

### Callouts

[Callout blocks](https://quarto.org/docs/authoring/callouts.html), such as @tip-example, can be useful for highlighting content, such as one might do in a box that defines key terms, etc.

::: {#tip-example .callout-tip}
#### All kinds of markup
Markdown: `*italics*, **bold text**, ~subscript~, ^superscript^ & ~~strikethrough~~`

renders as

*italics*, **bold text**, ~subscript~, ^superscript^ & ~~strikethrough~~
:::

### Code listings

Code listings can also be cross-referenced. @lst-r shows some great R [@rcoreteamLanguageEnvironmentStatistical2025] code.

```{r}
#| lst-label: lst-r
#| lst-cap: R code example.
#| collapse: true

sqrt(1 + 1)
```

# References

:::{#refs}
:::

::: {.appendix}

# Appendix A: Testing {.appendix}

Appendices have appropriate float references like @fig-3, @tbl-3, @lst-app, and @tip-appendix.

::: {#fig-3}
{{< placeholder 200 100 format=svg >}}
:::

::: {#tbl-3}
{{< placeholder 200 100 format=svg >}}
:::

```{r}
#| lst-label: lst-app
#| lst-cap: R code.
#| collapse: true

sqrt(1 + 1)
```

::: {#tip-appendix .callout-tip}
Appendices are an experimental feature
:::

Equations (@eq-app) work too but their numbering needs fixing.

$$
f(x \mid \mu, \sigma^2) = \frac{1}{\sqrt{2\pi \sigma^2}} \exp\left(-\frac{(x-\mu)^2}{2\sigma^2}\right)
$$ {#eq-app}

:::
